H2 Supplement

### 2023-02-06 supp_H2.Rmd
made plots smaller for  viewing (rather than download)

ggsave("plots/age_internalization.png", g1, width = 40, height = 25, units = "in", dpi = 300)

@@

ggsave("plots/age_symbolization.png", g1, width = 40, height = 25, units = "in", dpi = 300)

>>>>

ggsave("plots/age_internalization.png", g1, width = 30, height = 20, units = "in", dpi = 300)

@@

ggsave("plots/age_symbolization.png", g1, width = 30, height = 20, units = "in", dpi = 300)
